An Automatic Verification Framework for Software Configurations

### 2016-05-08 OSDI/intro.tex
more comments

In order to truly achieve automatic configuration verification,
we argue that we need to leverage a collection of more powerful learning 
algorithms (not necessarily depending on templates) to derive 
a more sophisticated language model (with abundant rules covering
tricky configuration errors), and then check the configuration files
of interest through the learned language model.

Based on the above argument, 
this paper presents \app, the first automatic verification framework
for general software configurations.
In particular, \app's workflow to verifying a given configuration file
could be looked as a three-step methodology.
First, \app analyzes a dataset containing sample configuration files,
thus generating a well-structured and probabilistically-typed 
intermediate representation.
Second, \app derives rules and constraints by analyzing
the intermediate representations, thus building a language model.
Finally, \app uses the resulting language model
to verify the given configuration file and detect potential errors.
Compared with previous efforts,
\app does not necessarily rely on users' templates, 
and is capable of detecting more tricky configuration errors that
cannot be identified by existing work (details in $\S$\ref{sec-motiv}).

Building such an automatic verification framework for
configuration files, nevertheless, requires addressing several challenges. 
First, in order to formulate a correct language model, 
we need to infer each entry's type in a given configuration file;
however, the type of a variable cannot always be fully determined 
from a single value. 
For example, an entry {\tt foo = MAX\_SIZE} is most likely
an integer rather than string; however, existing type inference 
work would report this is an error, because foo should be assigned
an integer~\cite{zhang14encore}. We address this problem by introducing 
so called {\emph{probabilistic types}}.
Rather than assigning only one variable to a single type, 
we assign several types with their probability distributions. 
The entry in the above example might be assigned 
a probabilistic type like 
{\tt \{foo, MAX\_SIZE, [(Int, 60\%), (String, 40\%)]\}}.
With such probabilistic types in hand,
we can generate a more accurate language model,
thus significantly improving our checking capability.

>>>>

In order to truly achieve automatic configuration verification,
we argue that we need to leverage a collection of more powerful learning 
algorithms (not necessarily depending on templates) to derive 
a more sophisticated language model (with abundant rules covering
tricky configuration errors), and then check the configuration files
of interest through the learned language model. \jon{Too many parentheses in setence. Cut down}

Based on the above argument, 
this paper presents \app, the first automatic verification framework
for general software configurations.
In particular, \app's workflow for verifying a given configuration file
can be viewed as a three-step methodology.
Firstly, \app analyzes a dataset containing sample configuration files,
thus generating a well-structured and probabilistically-typed 
intermediate representation.
Secondly, \app derives rules and constraints by analyzing
the intermediate representations, thus building a language model.
Finally, \app uses the resulting language model
to verify the given configuration file and detect potential errors.
Compared with previous efforts,
\app does not necessarily rely on users' templates 
and is capable of detecting tricky configuration errors that
cannot be identified by existing work (details in $\S$\ref{sec-motiv}).

Building such an automatic verification framework for
configuration files, nevertheless, requires addressing several challenges. 
Firstly, in order to formulate a correct language model, 
we need to infer each entry's type in a given configuration file, but 
the type of a variable cannot always be fully determined 
from a single value. 
For example, an entry {\tt foo = MAX\_SIZE} is most likely
an integer rather than string; however, existing type inference 
work would report this is an error, because {\tt foo} should be assigned
an integer~\cite{zhang14encore}. \jon{Unclear what the error is. Be more precise} We address this problem by introducing 
so called {\emph{probabilistic types}}.
Rather than assigning only one variable to a single type, 
we assign several types with their probability distributions. 
The entry in the above example might be assigned 
a probabilistic type like 
{\tt \{foo, MAX\_SIZE, [(Int, 60\%), (String, 40\%)]\}}.
With such probabilistic types in hand,
we can generate a more accurate language model,
thus significantly improving our checking capability.
